Title

### 2020-12-11 documents/DraftReport.Rmd
eval = F

```{r figures - multiple chains, results = 'hide', cache = F}

@@

```{r summary table}

@@

```{r plots, fig.height = 8.5, fig.width = 7, fig.align = 'center'}

@@

`r tbls("rmse_summary", caption = "Table of RMSE by scenario.")`
```{r table}

>>>>

```{r figures - multiple chains, eval = F, results = 'hide', cache = F}

@@

```{r summary table, eval = F}

@@

```{r plots, eval = F, fig.height = 8.5, fig.width = 7, fig.align = 'center'}

@@

`r tbls("rmse_summary", caption = "Table of RMSE by scenario.")`
```{r table, eval = F}
